r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2021-10-19 r-package/paper2021/paper2021.Rmd
Fixed paper Rmd: na.omit() was removing too many rows of the data.frame

# select trips departing the bus central station and add coordinates of destinations
travel_times <- ttm[fromId %in% central_bus_stn$id]
travel_times[points, on=c('toId' ='id'), `:=`(lon = i.lon, lat = i.lat)]

>>>>

# select trips departing the bus central station and add coordinates of destinations
travel_times <- ttm[fromId %in% central_bus_stn$id]
travel_times <- travel_times[, .(fromId, toId, travel_time_p050)]
travel_times[points, on=c('toId' ='id'), `:=`(lon = i.lon, lat = i.lat)]
